\providecommand{\itd}{..}
\documentclass[../ITD.tex]{subfiles}

\begin{document}
    \chapter{Development frameworks}\label{ch: development-frameworks}
    In the following chapter is presented a list of the frameworks and technologies used to develop SafeStreets system.
    \section{Adopted programming language}\label{sec:adopted-programming-laguage}
    The programming languages that have been used are:
    \subsection{Dart}\label{subsec:dart}
    Dart is an object-oriented, class-based, client-optimized programming language used to build apps on multiple platform.
    It has been used as language of the whole system, because of its support of Flutter framework.
    \newline
    \textbf{Advantages}
    \begin{itemize}
        \item Flutter support: the main pro in the choice of dart is the support of flutter framework.
        \item Object-oriented: allow to create a modular program and simplify code reusability.
        \item Ahead of time: dart is ahead of time compiled to fast and predictable native code, to make it fast and fully customizable.
        \item Just in time: dart can be just-in-time compiled for an exceptionally fast development cycle.
        \item Secure: the dart language, compiler, interpreter, and runtime environment were each developed with security as objective.
    \end{itemize}

    \textbf{Disadvantages}
    \begin{itemize}
        \item Maturity: not as mature as other programming languages, like java.
    \end{itemize}

    \section{Adopted middle-wares}\label{sec:adopted-middle-wares}
    \subsection{Flutter}\label{subsec:flutter}
    Flutter is an user interface development kit developed by Google used to build application for multiple systems (mobile, web and desktop) from a single codebase.
    It is based on Dart programming language.
    \newline
    \textbf{Advantages}
    \begin{itemize}
        \item Hot reload: it is possible to see the changes made to the code right away in the app.
        \item Cross platform: flutter can be used to build applications for different platform with just one codebase.
        \item Widgets: flutter takes everything on a widget approach, modeling and making everything intuitive.
        \item Google support: since flutter has been developed by Google, it gives an easy and optimized interaction with the other Google products.
    \end{itemize}

    \textbf{Disadvantages}
    \begin{itemize}
        \item Maturity: even if the flutter is supported by Google that provides all its feature and many useful libraries, the framework is relatively new, so it may miss something compared with some older one.
    \end{itemize}

    \subsection{Firebase}\label{subsec:firebase}
    Firebase is a Google's mobile platform that allows to store and synchronize data from web applications and mobile apps.
    It is a NoSQL database with great resources, high availability and that can be quickly integrated into other software projects.
    Firebase stores data as huge JSON file document with dynamic schema.
    It provides both a data and file database, and since it does not store data in table like the usual relational databases, it is more flexible to store different type of information.
    \newline
    \textbf{Advantages}
    \begin{itemize}
        \item Easy implementation: Firebase is thought to be implemented in mobile and web application, so it perfectly fits in the context of SafeStreets.
        \item Scalability: Firebase can easily scale in terms of size, virtually to infinity since it is provided by Google.
        \item Data synchronization: Firebase can instantly update data, making it powerful in the context of the application.
        \item Secure: data stored in Firebase are periodically backed up and always encrypted when are managed.
        \item Cost reduction: Firebase allows to bypass the managing of backend databases and corresponding hardware.
        \item User interface: it is possible to access to data via user interface.
    \end{itemize}
    \textbf{Disadvantages}
    \begin{itemize}
        \item Limited querying capabilities: since the database is implemented as a single file, it is not possible to define relation like in a classic relational database, and because of that complex query are more difficult to be managed.
    \end{itemize}

    \subsection{Mockito}\label{subsec:mokito}
    Mockito is a mocking framework used for testing.
    The framework is used to unit test the code with the help of Junit.
    Moreover, it allows the creation of test double object (mock objects) in automated unit tests for the purpose of test-driven development.

    \section{Additional APIs}\label{sec:additional-apis}
    \subsection{Google Maps}\label{subsec:google-maps}
    Google Maps is Google's web mapping service.
    It is one of the most accurate mapping service, and it can be easily integrated with Flutter since both of them have been developed by Google.
    \subsection{Plate Recognizer}\label{subsec:plate-recognizer}
    Plate Recognizer is a web service used to find the plates in a picture.
    It can spot the position of the plates and read them, and works with the plats of almost every country in the world.

\end{document}