\providecommand{\atd}{..}
\documentclass[../ATD.tex]{subfiles}

\begin{document}
    \chapter{Application and document analysis}\label{ch:application-and-document-analysis}
    \section{Application analysis}\label{sec:application-analysis}
    \subsection{Features analysis}\label{subsec:feature-analysis}
    In these section we want to provide a recap of the feature of the system that work correctly, partially work or do not work at all.
    \newline
    \textbf{Working features}
    \begin{itemize}
        \item User log-in
        \item Municipality log-in
    \end{itemize}
    \newline
    \textbf{Partially working feature}
    \begin{itemize}
        \item Municipality violation query
    \end{itemize}
    \newline
    \textbf{Not working feature}
    \begin{itemize}
        \item Registration
        \item Violation reporting
        \item Statistics querying
        \item Map visualization
    \end{itemize}
    \subsection{Requirement analysis}\label{subsec:requirement-analysis}
    Here is presented a table to recap which requirements pass the tests and which do not.

    \begin{enumerate}
        \requirement{1} The reports about the violations are correctly stored.
        \requirement{2} The user can view the statistics calculated by the system with some exceptions.
        \requirement{3} The municipality can access only the data of the violations of its competence area.
        \requirement{4} Violations registered by the municipality can be retrieved by the system.
        \requirement{5} The system must avoid the manipulation of the violations.
        \requirement{6} The system must be able to retrieve the position from the user or from the GPS.
        \requirement{7} Only the municipality can access the submitted parking violation of its competence area.
        \requirement{8} The system must allow the user to take a picture or to select one from the device.
        \requirement{9} The system accepts reports from the user.
        \requirement{10} The system must calculate some statistics.
        \requirement{11} The municipality can view all the statistics calculated by the system.
        \requirement{12} The system must suggest interventions to the municipality.
        \requirement{13} The system accepts only reports with a valid plate number and position.
        \requirement{14} The system must allow the user to perform the registration and the login.
        \requirement{15} The system must allow the municipality to perform the registration and the login.
        \requirement{16} The system must ask the user the non-mandatory attributes of the report.
        \requirement{17} The system must communicate with the Identity Verifier.
        \requirement{18} The system must communicate with the Plate Recognizer Service.
        \requirement{19} The system must communicate with the Maps Service.
    \end{enumerate}
    %%traceability matrix
    \begin{adjustwidth}{+2cm}{}
        \begin{longtable}[H]
        {|| p{.10\linewidth} || p{.40\linewidth} ||
        p{.19\linewidth} | p{.13\linewidth} |}
            \hline
            \textbf{\makecell{R}} & \textbf{\makecell{Satisfied}} \\ \hline
            \textbf{1}  & \textit{Untestable}  \\ \hline
            \textbf{2}  & \textit{No}          \\ \hline
            \textbf{3}  & \textit{Yes}         \\ \hline
            \textbf{5}  & \textit{Yes}*        \\ \hline
            \textbf{6}  & \textit{Untestable}  \\ \hline
            \textbf{7}  & \textit{No}          \\ \hline
            \textbf{8}  & \textit{Yes}         \\ \hline
            \textbf{9}  & \textit{No}          \\ \hline
            \textbf{10} & \textit{Untestable}  \\ \hline
            \textbf{11} & \textit{No}          \\ \hline
            \textbf{13} & \textit{Untestable}  \\ \hline
            \textbf{14} & \textit{Partially}** \\ \hline
            \textbf{15} & \textit{Partially}** \\ \hline
            \textbf{16} & \textit{Untestable}  \\ \hline
            \textbf{19} & \textit{Untestable}  \\ \hline
            \caption[\textit{Traceability matrix}]{\textit{Traceability matrix}}
        \end{longtable}
    \end{adjustwidth}
    * : Some data are showed wrong in the municipality violation query.
    \newline
    **: Only login requirement is satisfied.


    \section{Test analysis}\label{sec:test-analysis}

    %todo ---------

    \section{Document analysis}\label{sec:document-analysis}

    %todo----------


\end{document}